\documentclass[letterpaper, 11pt]{article}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{times}
%\usepackage[in]{fullpage}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{graphicx}

%\documentclass[11pt]{article}
%\pagestyle{myheadings}
\usepackage[ruled,nothing]{algorithm}
\usepackage{algorithmic}
%\usepackage[dvips]{epsfig,graphicx}
%\numberwithin{equation}{section}

\bibliographystyle{plain}

\setlength{\parindent}{0em}
\setlength{\parskip}{1em}


\begin{document}

\title{Homework \#6 \\ Introduction to Algorithms \\ 601.433/633 \\ Spring 2020}
\author{\textbf{Due on:} Tuesday, April 21st, 12pm \\}
\date{}
\vspace{-1cm}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem 1 (15 points)}
Let $G = (V, E)$ be an undirected graph with \emph{distinct non-negative} edge weights.
Consider a problem similar to the single-source shortest paths problem, but where
we define path cost differently. We will define the cost of a simple $s$-$t$ path $P_{s,t} =
\{e_1, e_2, \ldots, e_k\}$ to be $$c(P_{s,t}) = \max_{e \in P} w_e$$

The cost of a path is now just the largest weight on that path, rather than the
sum of the weights on the path. Give an algorithm that takes as input an undirected
graph $G = (V, E)$ with \emph{non-negative edge weights}, and a vertex $s \in V$, and
computes the path from $s$ to every other node in $G$ with the least cost under cost
function $c(\cdot)$. That is, for each $t \in V$ , find a simple path $P_{s,t} =
\{(s, v_1), (v_1, v_2), \dots, (v_{k-1}, v_k), (v_k, t)\}$ connecting $s$ to $t$, such that, letting $S$ denote the set of all simple paths connecting $s$ and $t$, $c(P_{s, t}) = \min_{P\in S} c(P)$. 

Your algorithm should run in $O(|E| + |V| \log |V|)$ time. Prove the correctness of your algorithm and its runtime. Hint: note the similarities between Dijkstra's algorithm and Prim's
algorithm.





\section{Problem 2 (15 points)}

You are given a simple weighted graph (no self-edges or multi-edges) $G = (V, E)$ and its minimum spanning tree $T_{\text{mst}}$. Somebody added a new edge $e$ to the graph $G$. Let's call new graph $G' = (V, E\cup \{e\})$. Devise an algorithm which checks if $T_{\text{mst}}$ is also a minimum spanning tree for the graph $G'$ or not. Your algorithm should work in $O(|V|)$ time. Prove correctness of your algorithm and provide running time analysis.

You can assume that all edge weights in $G'$ are distinct. $T_{\text{mst}}$ and $G'$ are given to you as adjacency lists.






\section{Problem 3 (20 points)}
An airline has $n$ flights. In order to avoid ``re-accommodation'', a passenger must satisfy several requirements. Each requirement is of the form ``you must take at least $k_i$ flights from set $F_i$''. The problem is to determine whether or not a given passenger will experience ``re-accommodation''. The hard part is that any given flight cannot be used towards satisfying multiple requirements. For example, if one requirement states that you must take at least two flights from $\{A,B,C\}$, and a second requirement states that you must take at least two flights from $\{C,D,E\}$, then a passenger who had taken just $\{B,C,D\}$ would not yet be able to avoid ``re-accommodation''.

Given a list of requirements $r_1,r_2,\dots,r_m$ (where each requirement $r_i$ is of the form: ``you must take at least $k_i$ flights from set $F_i$''), and given a list $L$ of flights taken by some passenger, determine if that passenger will experience ``re-accommodation''. Your algorithm should run in $O(|L|^2m)$ time.

Hint: You should just need to show how this can be reduced to a network flow problem and then use a blackbox algorithm solving the flow problem. Prove that your reduction is correct and that the runtime of the algorithm you use will be $O(|L|^2m)$ for the reduction you give.



\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
